A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
updated paper.tex, removed final_paper.tex
Add in table
added figure benchmark
added improvment graph
added bench graphs

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}

@@

We attempted to measure the

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=160mm]{lr-10.png}
  \caption{}
\end{figure}

>>>>

\title{A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing}
\author{
        Russell Cohen \\
            \and
        Thomas Georgiou \\
            \and
        Pedram Razavi
}
\date{\today}
\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{float}

@@

We attempted to measure the 
 \begin{figure}[H]
   \centering
   \includegraphics[width=5in]{tables.pdf}
   \caption{}
 \end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm]{appsbench.pdf}
  \caption{Prcentage of overall improvements in some real-world Python applications. Nearly none of the applications performed worse. Python Pickle and html5lib faster around \%3 to \%4. }
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm]{slowpickle.png}
  \caption{Python Pickle module benchmark. Minimum Iteration: changed from 0.705s to 0.681s: 1.04 times faster. Average iteration: changed from 0.710s to 0.686s: 1.04 times faster. Standard deviation of new implementation 2.0383 times smaller}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=160mm]{lr-10.png}
%   \caption{}
% \end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=160mm]{lr-10.png}
%   \caption{}
% \end{figure}
